Hybrid Threads for the Parrot Virtual Machine

### 2012-03-09 Paper.tex
Another typo
tadzik++

Following is a simple example to explain why concurrent processing can endanger the interpreter's internal consistency. The basic problem is concurrent writes to shared data. Assumeing an implementation of an array class consisting of the field holding the data and the number of contained elements in a seperate member variable:
\begin{CCode}
pmclass ResizableIntegerArray auto_attrs provides array {
    ATTR INTVAL   size;      /* number of INTVALs stored in this array */
    ATTR INTVAL * int_array; /* INTVALs are stored here */
\end{CCode}
to append a new value, the array would have to read the current size, write the new value at the position size + 1 and then write the incremented size back into the member variable.
Now if two threads simultainously try to do this, it may happen that both read the same size, write to the same position (with one overwriting the value of the other) and write back the same incremented size. In this case one of the appended values would be lost.

>>>>

Following is a simple example to explain why concurrent processing can endanger the interpreter's internal consistency. The basic problem is concurrent writes to shared data. Assuming an implementation of an array class consisting of the field holding the data and the number of contained elements in a seperate member variable:
\begin{CCode}
pmclass ResizableIntegerArray auto_attrs provides array {
    ATTR INTVAL   size;      /* number of INTVALs stored in this array */
    ATTR INTVAL * int_array; /* INTVALs are stored here */
\end{CCode}
to append a new value, the array would have to read the current size, write the new value at the position size + 1 and then write the incremented size back into the member variable.
Now if two threads simultainously try to do this, it may happen that both read the same size, write to the same position (with one overwriting the value of the other) and write back the same incremented size. In this case one of the appended values would be lost.
